Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-10 acl.2016/acl2016.tex
oov penalty

\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{scalability.png}} 
\end{tabular}
\caption{Our decoder's decoding speed}
\label{fig:speed}
\end{figure}

Showing decoding \emph{speed} rather than decoding time better illustrate the scalability of our approach. Figure~\ref{fig:speed} shows decoding speed against the number of threads, measured in words translated per second. There is a constant increase in decoding speed when more threads are used, decreasing slightly after 16 threads when virtual cores are employed by the CPU. Overall, decoding is 12.5 times faster than single-threaded decoding when all 16 cores (32 hyperthreads) are fully utilized.

@@

This contrast with Moses where speed increases to approximately 16 threads but then actually become slower thereafter, Figure~\ref{fig:moses-speed}. Using the tcmalloc library has a small positive effect on decoding speed but does little to improve scalability 
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{moses-scalability.png}} 
\end{tabular}
\caption{Moses' decoding speed}
\label{fig:moses-speed}
\end{figure}

@@

Our work is 4.5 times faster than Moses with a single-thread and 9.6 faster when all cores are used.

>>>>

\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{scalability.png}} 
\end{tabular}
\caption{Comparison of decoding speed of our work and Moses (with \& without the tcmalloc library}
\label{fig:speed}
\end{figure}

Figure~\ref{fig:speed} shows decoding speed against the number of threads used. In our work, there is a constant increase in decoding speed when more threads are used, decreasing slightly after 16 threads when virtual cores are employed by the CPU. Overall, decoding is 16 times faster than single-threaded decoding when all 16 cores (32 hyperthreads) are fully utilized.

@@

This contrast with Moses where speed increases to approximately 16 threads but then actually become slower thereafter. Using the tcmalloc library has a small positive effect on decoding speed but does little to improve scalability 
%\begin{figure}[h]
%\centering
%\begin{tabular}{cc}
%{\includegraphics[scale=0.5]{moses-scalability.png}} 
%\end{tabular}
%\caption{Moses' decoding speed}
%\label{fig:moses-speed}
%\end{figure}

@@

Our work is 4.3 times faster than Moses with a single-thread and 10.4 faster when all cores are used.
